Kelompok 4_Praktikum_Pekan 8

### 2024-04-06 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r, fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
hist(normal_means, main = "Histogram Normal Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#8DC16D")
hist(uniform_means, main = "Histogram Uniform Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#4493CA")
hist(exponential_means, main = "Histogram Exponential Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#D44155")
```

@@

```{r, fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(norm_means, main = "Normal QQ Plot", col = "#8DC16D", lwd = 5,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means, col = "red", lwd=2)

>>>>

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
hist(normal_means, main = "Histogram Normal Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#8DC16D")
hist(uniform_means, main = "Histogram Uniform Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#4493CA")
hist(exponential_means, main = "Histogram Exponential Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#D44155")
```

@@

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(norm_means, main = "Normal QQ Plot", col = "#8DC16D", lwd = 5,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means, col = "red", lwd=2)
